\thesistitle

### 2019-06-12 sections/research.tex
Type 2R threshold

\subsubsection{A threshold for variability in literals, variables and method calls}

\subsubsection{Allow any change in some names}
- Names of method definitions
- Names of locally declared variables
- etc?

>>>>

\subsubsection{A threshold for variability in literals, variables and method calls}
Type 2 clones allow any variability in literals, variables and method identifiers. However, this information tells a lot about the meaning of the code fragment. Most clone detection tools do not differentiate between a type 2 clone that differs by a single literal/identifier and one that differs by many. However, this does have a big impact on the meaning of the code fragment and thus the harmfulness of the duplication being there.

For type 2R clones we define a threshold for variability in literals, variables and method calls. We calculate the variability in literals, variables and method calls using the following formula:

T2R Variability = (Diff(l) + Diff(v) + Diff(m))/Total(t)
Diff = Amount that differ from other clone instances in the clone class
Total = Total number in the clone instance
l = Number of literals
v = Number of variables
m = Number of method calls
t = Number of tokens

Looking at this formula, it becomes apparent that we made the decision to let literals, variables and method calls count towards the same threshold. So a large variability in method calls might constrain variability from literals. This is because how to refactor variability in literals, variables and method calls. When we use either a different literal, variable or method call, we will have to use a

\paragraph{Literal variability}

\subsubsection{Allow any change in some identifiers}
- Identifier of method declarations
- Identifier of locally declared variables
- Identifier of class/interface/enum declaration
- etc?
